Reducing retrieval error in MAIAC AOD with the `Earth_obs_cleaning` machine-learning workflow: Results from CONUS

### 2024-02-21 writing/paper_aodc.qmd
Added a SHAP figure for AODC.
Extended the AQS comparsion to AODC.

@@

>>>>

## SHAP interpretation

```{r shap_summary}
#| label: fig-shap-summary
#| fig-cap: Summary of SHAP contributions. Predictors ordered by decending mean absolute SHAP (printed along left).
IG(tar_read(shap.summary.plot.path))
```

@@

## Comparison with AQS PM~2.5~

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$n.aqs.obs)` observations of AQS PM~2.5~ in `r scales::comma(l$n.cell.times)` cell-hours. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.

### 2024-02-21 writing/paper_mcd19a2.qmd
Got the MCD19A2 paper rendering again.
Extended the AQS comparsion to AODC.

@fig-map-improve-mse shows a tile on `r tar_read(improve.mse.map.data)$date`.

@@

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$nobs)` observations of AQS PM~2.5~ on `r scales::comma(l$celldays)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.

>>>>

@fig-map-median-improve shows a tile on `r tar_read(median.improve.map.data)$date`.

@@

We examined `r l = tar_read(satellite.vs.aqs); scales::comma(l$n.aqs.obs)` observations of AQS PM~2.5~ on `r scales::comma(l$n.cell.times)` cell-days. The correlation of the observations with the original satellite values was `r sprintf("%.03f", l$old)`, compared to `r sprintf("%.03f", l$new)` with our corrected values.
